---
title: "Outreachy datascience 2019"
author: "Ana Laura Diedrichs"
date: "October 1, 2019"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dataset

Import the dataset first.
```{r cars, echo=FALSE}
library(readr)
dataset <- read_csv("dataset.csv")

```

The dataset has `r ncol(dataset)` varibles (columns) and `r nrow(dataset)` observations (rows). 

Let's give a first look:

```{r}
head(dataset)
```

The column Id is not a variable for the problem, so I proceed to deleted it.

```{r}
dataset <- dataset[-1]
```

```{r}
library(DataExplorer)
t(introduce(dataset) )
```

Some insights:

* We have some missing values
* The dataset has a mix of categorical and numerical variables
* We don't have completed rows, where all the values for the same row are not NULL or NaN or not missing.

As a first step, we are going to analyze the missing values.

### Missing values 

```{r}
library(dplyr) # for dataset processing + pipe operator

missing_report <- dataset %>% 
                  profile_missing() %>% 
                  filter(num_missing >0) %>%
                  as_data_frame() %>%
                  arrange(desc(pct_missing)) #order rows by column pct_missing

missing_report
```

The first four features listed above, have more than 80% of missing values. I proceed to ignore that features because I find it hard to reconstruct them (imputation) with few data.

The columns I'm going to drop are:
```{r}
drop_columns <- as.character(missing_report$feature[1:4])

drop_columns
```

I drop the columns from the dataset

```{r}
dataset <- dataset %>% 
  select(-one_of(drop_columns)) 
```

Our dataset has left now four columns/variables, and now we have `r ncol(dataset)` columns.


## Valid variable names

Function make names convert columns names to valid variable names. There are some functions that convert the column name (a string) as a variable, so we want to avoid 
sintax errors later.

```{r}
new.names <- make.names(colnames(dataset))
```


What are the names that where replaced ?
```{r}

colnames(dataset)[!new.names %in% colnames(dataset)]
```

We can see that area some variables names which start with a number. 

So the new names are:

```{r}
new.names
```

The columns names 3SsnPorch, 1stFlrSF, 2ndFlrSF where replaced by X3SsnPorch, X1stFlrSF, X2ndFlrSF.

So, we renamed the columns of our dataset.

```{r}
colnames(dataset) <- new.names
```

## Correlation 

I would like to know if we have highly correlated features related with Sales Price.

### Continuous variables

```{r}
num_dataset <- dataset %>% 
  select_if( is.numeric) %>% scale()

plot_correlation(num_dataset, cor_args = list("use" = "pairwise.complete.obs"))
```
```{r}
library(tidyverse)
cor(num_dataset) %>% # calculate correlations using Pearson
  as.data.frame() %>%
  mutate(var1 = rownames(.)) %>%
  gather(var2, value, -var1) %>%
  arrange(desc(value)) %>% 
  group_by(value) %>% 
  filter(row_number()==1) %>%
  filter(var1 == "SalePrice")

```

SalePrice and OverallQual

```{r}
plot(dataset$OverallQual,dataset$SalePrice)
```

### SmartEDA package

```{r,echo=FALSE}
report_name <- "EDA_report_1.html"
```

The following line create a complited EDA report for the dataset. It took a while to run in a PC celeron computer. The report is saved as `r report_name`

```{r, eval=FALSE}
library(SmartEDA)
library (ggthemes)
ExpReport(dataset,Target = "SalePrice",op_file=report_name,Rc="continuous",sc=2,sn=2)
```
```{r}
library(SmartEDA)
ExpData(dataset,type=2)
```



### Categorical variables
Analysis of predictivity power of categorical variables over SalePrice column.


```{r}
library(SmartEDA)
ExpCatStat(dataset,Target="SalePrice")
```

Filter to let only varibles with some predictive power

```{r}

```
# Referencias

Leer sobre correlacion https://medium.com/@outside2SDs/an-overview-of-correlation-measures-between-categorical-and-continuous-variables-4c7f85610365

